Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-31 article/03_Results.Rmd
small changes in the light of new results

Table \ref{tab:dactb} shows that the distance networks of *burial type* and *burial construction* are not equivalent. There is also no significant negative correlation. The degree of agreement between two regions in the question of inhumation and cremation is therefore not suitable for predicting the similarity of developments in these regions concerning the dominance of flat or mound graves. Only for the time slot at the transition to the Middle Bronze Age from 1800 to 1600 calBC the 5% significance level of the Mantle test is almost undercut, thus suggesting a statistically significant relationship. This moment of strong correlation is though not induced by similarity along the spatial dimension: The effect is still visible in the result of the Partial Mantel test, where the spatial distance is artificially counterbalanced.

>>>>

Table \ref{tab:dactb} shows that the distance networks of *burial type* and *burial construction* are not equivalent. There is also no significant negative correlation. The degree of agreement between two regions in the question of inhumation and cremation is therefore not suitable for predicting the similarity of developments in these regions concerning the dominance of flat or mound graves. Only for the time slot at the transition to the Middle Bronze Age from 1800 to 1600 calBC the 5% significance level of the Mantle test is almost undercut, thus suggesting a statistically significant relationship. This moment of strong correlation is though not induced by similarity along the spatial dimension: The effect is still visible in the result of the Partial Mantel test, where the spatial distance is artificially counterbalanced (Figure \ref{correlationtimeseries}).

### 2019-03-31 article/04_Discussion.Rmd
small changes in the light of new results

Against this background, the observation that there is no permanent, significant correlation either between the variables or with the spatial distance is all the more astonishing (Table \ref{tab:dacta}). Only for small periods of time this correlation is visible in the Radon-B data. The *burial construction* distance shows a higher degree of correlation with spatial distance than the *burial type* distance, which even seems to behave in an opposing manner: negative correlation. If one assumes the reconstructed timelines of cultural similarity intensity to be correct, than one has to explain a rise (between 2200 and 2000 calBC) and a decline (after 2000 calBC) of cultural-spatial-distance correlation. There are several reasons why any interpretation of this observation is difficult so far:

>>>>

Against this background, the observation that there is no permanent, significant correlation either between the variables or with the spatial distance is all the more astonishing (Table \ref{tab:dacta} & \ref{tab:dactB} & Figure \ref{correlationtimeseries}). Only for certain periods of time this correlation is visible in the Radon-B data. The *burial construction* distance shows a higher degree of correlation with spatial distance than the *burial type* distance, which even seems to behave in an opposing manner: negative correlation. If one assumes the reconstructed timelines of cultural similarity intensity to be correct, than one has to explain a rise (between 2200 and 2000 calBC) and a decline (after 2000 calBC) of cultural-spatial-distance correlation. There are several reasons why any interpretation of this observation is difficult so far:
